---
title: "Figures for CEA of DSD manuscript"
output: html_document
date: "2023-07-14"
---

Code of all figures in the CEA of DSD paper

Date last modified: Nov 10.

Content

- Figure 1: Incidence, prevalence, mortality, and ART coverage

- Figure 2: ICERs of DSD vs. SoC (sim length is 40 years)

- Figure 3: ICER of DSD vs. SoC by time horizons

- Figure 4: One-way sensitivity analysis

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Figure 1: Incidence, prevalence, mortality, and ART coverage
```{r func-epi-plots}
rm(list=ls()) # clear the work space

library(ggplot2)
library(tidyverse)
library(gridExtra)
library(grid)
library(cowplot)
```

### Functions
```{r}
# plot incidence + prevalence + mortality + ART coverage plot for a single country under four scenarios (SoC, CAG, homeART, UAG)
# output_width: the width of the output graph
# output_height: the height of the output graph
# legend_pos: position of legend
plot_one_country = function(file_name, country_name, output_width=2.5, output_height=8, legend_pos='none',
                            col_SoC="#F8766D", col_CAG="#00BFC4", col_HomeART="#619CFF", col_UAG="#C77CFF", 
                            label_names=c("SoC", "CAGs", "HomeART", "UAGs")){
  path = paste0("Figure1/", file_name)
  df <- read.csv(path)
  
  # Reshape to long format
  df_inci <- df %>%
    pivot_longer(cols = starts_with("inci_"), names_to = "DSDModality", values_to = "Incidence") %>%
    select(Year, DSDModality, Incidence)
  df_prev <- df %>%
    pivot_longer(cols = starts_with("prev_"), names_to = "DSDModality", values_to = "Prevalence") %>%
    select(Year, DSDModality, Prevalence)
  df_mort <- df %>%
    pivot_longer(cols = starts_with("mort_"), names_to = "DSDModality", values_to = "Mortality") %>%
    select(Year, DSDModality, Mortality)
  df_art <- df %>%
    pivot_longer(cols = starts_with("art_"), names_to = "DSDModality", values_to = "ARTCov") %>%
    select(Year, DSDModality, ARTCov)
  
  # Incidence
  plot1=ggplot(df_inci, aes(x = Year, y = Incidence, color = DSDModality)) +
  geom_line() +
  labs(x = "Year", y = "Incidence/100PY", title = "Incidence") +
  scale_color_manual(values = c("inci_00" = col_SoC, "inci_25" = col_CAG, "inci_38" = col_HomeART, "inci_50" = col_UAG),
                     labels = label_names) +
    ylim(0, 2) + theme_minimal() +
    theme(legend.position = legend_pos, plot.title = element_text(size = 9), axis.title = element_text(size = 7))
  
  # Prevalence
  plot2=ggplot(df_prev, aes(x = Year, y = Prevalence, color = DSDModality)) +
  geom_line() +
  labs(x = "Year", y = "Prevalence", title = "Prevalence") +
  scale_color_manual(values = c("prev_00" = col_SoC, "prev_25" = col_CAG, "prev_38" = col_HomeART, "prev_50" = col_UAG),
                     labels = label_names) +
    scale_y_continuous(limits = c(0, 0.18)) + theme_minimal()+
    theme(legend.position = legend_pos, plot.title = element_text(size = 9), axis.title = element_text(size = 7))
  
  # Mortality
  plot3=ggplot(df_mort, aes(x = Year, y = Mortality, color = DSDModality)) +
  geom_line() +
  labs(x = "Year", y = "Mortality/1000 PLHIV", title = "Mortality among PLHIV") +
  scale_color_manual(values = c("mort_00" = col_SoC, "mort_25" = col_CAG, "mort_38" = col_HomeART, "mort_50" = col_UAG),
                     labels = label_names) +
    scale_y_continuous(limits = c(0, 80)) + theme_minimal() +
    theme(legend.position = legend_pos, plot.title = element_text(size = 9), axis.title = element_text(size = 7))
  
  # ART coverage
  plot4=ggplot(df_art, aes(x = Year, y = ARTCov, color = DSDModality)) +
  geom_line() +
  labs(x = "Year", y = "ARTCov", title = "ART coverage among PLHIV") +
  scale_color_manual(values = c("art_00" = col_SoC, "art_25" = col_CAG, "art_38" = col_HomeART, "art_50" = col_UAG),
                     labels = label_names) +
    ylim(0, 1) + theme_minimal() +
    theme(legend.position = legend_pos, plot.title = element_text(size = 9), axis.title = element_text(size = 7))
  
  grid.arrange(plot1, plot2, plot3, plot4, nrow=4, top = textGrob(country_name, gp=gpar(fontsize=10,font=2)))
  # ggsave(file=paste0("Figure1_EpiStates/", Sys.Date(), "-", country_name, ".png"), g, width = output_width, height = output_height) 
}
```

### Plot
```{r}
# legend position: right, left, top, bottom, none (default).
epi_lmic=plot_one_country(file_name = "LMIC.csv", country_name = "LMICs", legend_pos = "right", output_width = 3.8, output_height=8)
epi_sa=plot_one_country(file_name = "SA.csv", country_name = "South Africa")
epi_zambia=plot_one_country(file_name = "Zambia.csv", country_name = "Zambia")
epi_malawi=plot_one_country(file_name = "Malawi.csv", country_name = "Malawi")

# combine all plots and create common legend
grid.arrange(epi_sa, epi_zambia ,epi_malawi, epi_lmic, 
             layout_matrix=rbind(c(1,1,2,2,3,3,4,4,4)))
g <- arrangeGrob(epi_sa, epi_zambia ,epi_malawi, epi_lmic,
             layout_matrix=rbind(c(1,1,2,2,3,3,4,4,4)),
             top = textGrob("", gp=gpar(fontsize=16,font=2)))
ggsave(file=paste0("Figure1/", Sys.Date(), "-graph1", ".png"), g, width = 10, height =6) #saves g
```

# Figure 2: ICERs for DSD vs. SOC (sim-length=40 years)
### v1: by country
```{r setup_and_read_files}
rm(list=ls()) # clear the work space
library(ggplot2)
library(grid)
library(gridExtra)
library(cowplot)
```

##### Functions
```{r icer-plot-function}
# Country specific incremental cost and effectiveness plane
# WTP1 & WTP2: willingness-to-pay thresholds
plot_country_icer <- function(df, country_name, WTP1=500, WTP2=750, 
                              col_CAG = "#00BFC4", col_HomeART="#C77CFF", col_UAG = "#619CFF", col_WTP = "grey", col_baseline="black",
                              output_width=7, output_height=5, legend_position="none", xlim, ylim){
  icer.plot <- ggplot() +
  labs(y = "Incremental costs", x = "Incremental DALYs", title = country_name) + 
    theme_minimal() +
  coord_cartesian(xlim = c(0, xlim), ylim = c(0, ylim))
  
  icer.plot <- icer.plot +
    # CAG vs. SOC
    geom_point(data = df, aes(y = Diff_cpoint_cag_soc, x = Diff_dalys_cag_soc, color = "CAG"), alpha = 0.15, size = 1) + 
    geom_point(data = df, aes(y = median(Diff_cpoint_cag_soc), x = median(Diff_dalys_cag_soc), color = "CAG"), size = 4, shape = 18) +
    # UAG vs. SoC
    geom_point(data = df, aes(y = Diff_cpoint_uag_soc, x = Diff_dalys_uag_soc, color = "UAG"), alpha = 0.15, size = 1) + 
    geom_point(data = df, aes(y = median(Diff_cpoint_uag_soc), x = median(Diff_dalys_uag_soc), color = "UAG"), size = 4, shape = 18) +
    # Home ART vs. SoC
    geom_point(data = df, aes(y = Diff_cpoint_hom_soc, x = Diff_dalys_hom_soc, color = "HomeART"), alpha = 0.15, size = 1) + 
    geom_point(data = df, aes(y = median(Diff_cpoint_hom_soc), x = median(Diff_dalys_hom_soc), color = "HomeART"), size = 4, shape = 18) +
    # WTP lines
    geom_abline(slope = WTP1, intercept = 0, color = col_WTP, linetype = "dashed", alpha = 0.7) + 
    geom_abline(slope = WTP2, intercept = 0, color = col_WTP, linetype = "dashed", alpha = 0.7) +
    # baesline: y=0
    geom_hline(yintercept = WTP1, linetype = "dotted", color = col_baseline, linewidth=0.3)
  
  # add legend based on color
  icer.plot <- icer.plot +
    scale_color_manual(values = c(col_CAG, col_HomeART, col_UAG), guide = guide_legend(title = "DSD (vs. SoC)")) +
    theme_bw() + 
    theme(legend.position = legend_position,
          panel.grid = element_blank()) # remove grid
  # ggsave(file=paste0("Figure2/", Sys.Date(), "-", country_name, "_ICERs.png"), icer.plot, width = output_width, height = output_height)
}
```

##### Plot
```{r fig2-separate-plots}
# setup working directory
path <- getwd() # Retrieve the current folder path

# Read in files
malawi <- read.csv(paste0(path, "/Figure2/Malawi.csv"))
zambia <- read.csv(paste0(path, "/Figure2/Zambia.csv"))
sa <- read.csv(paste0(path, "/Figure2/SouthAfrica.csv"))
LMICs <- read.csv(paste0(path, "/Figure2/Synthesis.csv"))
icer_sa = plot_country_icer(df = sa, country_name = "SouthAfrica", WTP1=590, WTP2=3525, xlim=27000000, ylim=28000000000)
icer_zambia = plot_country_icer(df = zambia, country_name = "Zambia", xlim=6500000, ylim=4300000000)
icer_malawi = plot_country_icer(df = malawi, country_name = "Malawi", xlim=4000000, ylim=3000000000)
icer_lmic = plot_country_icer(df = LMICs, country_name = "LMICs", xlim=2500000, ylim=2000000000)

# get common legend
legend <- get_legend(plot_country_icer(df = malawi, country_name = "Malawi", output_width=7, output_height=5, legend_position="right", xlim=4, ylim=4))
# combine all plots and create common legend
grid.arrange(icer_sa, icer_zambia ,icer_malawi, icer_lmic, legend, 
             layout_matrix=rbind(c(1,1,2,2,5), c(3,3,4,4,5)))
g <- arrangeGrob(icer_sa, icer_zambia ,icer_malawi, icer_lmic, legend,
             layout_matrix=rbind(c(1,1,2,2,5), c(3,3,4,4,5)),
             top = textGrob("ICERs of DSD compared to SoC", gp=gpar(fontsize=16,font=2)))
ggsave(file=paste0("Figure2/", Sys.Date(), "-graph2-byCountry", ".png"), g, width = 9, height =6) #saves g
```

### v2: consolidate
```{r read_dataframes}
rm(list=ls()) # clear the work space
library(ggplot2)
library(grid)
library(gridExtra)
library(cowplot)

# setup working directory
path <- getwd() # Retrieve the current folder path

# Read in files
malawi <- read.csv(paste0(path, "/Figure2/Malawi.csv"))
zambia <- read.csv(paste0(path, "/Figure2/Zambia.csv"))
sa <- read.csv(paste0(path, "/Figure2/SouthAfrica.csv"))
LMICs <- read.csv(paste0(path, "/Figure2/Synthesis.csv"))
```

##### Plot
```{r fig2-all-in-one}
# ggplot point shape: http://www.sthda.com/english/wiki/ggplot2-point-shapes
WTP1 = 500
WTP2 = 750
sa_WTP1 = 590
sa_WTP2 = 3525
ALPHA = 0.1 # opacity
malawi_shape = 18
zambia_shape = 18
sa_shape = 18
lmic_shape = 18

icer.plot <- ggplot() +
  labs(y = "Incremental costs", x = "Incremental DALYs", title = "ICERs of DSD compared to SoC") + 
    theme_minimal()

# (another way is to first convert the data to long-format, and simplify code block below (as figure 3 v1))
# Malawi: CAG, UAG, HomeART
icer.plot <- icer.plot + 
  geom_point(data = malawi, aes(y = Diff_cpoint_cag_soc, x = Diff_dalys_cag_soc, color = "Malawi-CAG"), alpha = ALPHA, size = 1) + 
  geom_point(data = malawi, aes(y = median(Diff_cpoint_cag_soc), x = median(Diff_dalys_cag_soc), color = "Malawi-CAG"), size = 4, shape = malawi_shape) +
  geom_point(data = malawi, aes(y = Diff_cpoint_uag_soc, x = Diff_dalys_uag_soc, color = "Malawi-UAG"), alpha = ALPHA, size = 1) + 
  geom_point(data = malawi, aes(y = median(Diff_cpoint_uag_soc), x = median(Diff_dalys_uag_soc), color = "Malawi-UAG"), size = 4, shape = malawi_shape) +
  geom_point(data = malawi, aes(y = Diff_cpoint_hom_soc, x = Diff_dalys_hom_soc, color = "Malawi-HomeART"), alpha = ALPHA, size = 1) + 
  geom_point(data = malawi, aes(y = median(Diff_cpoint_hom_soc), x = median(Diff_dalys_hom_soc), color = "Malawi-HomeART"), size = 4, shape = malawi_shape) +
  
# Zambia: CAG, UAG, HomeART
geom_point(data = zambia, aes(y = Diff_cpoint_cag_soc, x = Diff_dalys_cag_soc, color = "Zambia-CAG"), alpha = ALPHA, size = 1) +
  geom_point(data = zambia, aes(y = median(Diff_cpoint_cag_soc), x = median(Diff_dalys_cag_soc), color = "Zambia-CAG"), size = 4, shape = zambia_shape) +
  geom_point(data = zambia, aes(y = Diff_cpoint_uag_soc, x = Diff_dalys_uag_soc, color = "Zambia-UAG"), alpha = ALPHA, size = 1) +
  geom_point(data = zambia, aes(y = median(Diff_cpoint_uag_soc), x = median(Diff_dalys_uag_soc), color = "Zambia-UAG"), size = 4, shape = zambia_shape) +
  geom_point(data = zambia, aes(y = Diff_cpoint_hom_soc, x = Diff_dalys_hom_soc, color = "Zambia-HomeART"), alpha = ALPHA, size = 1) +
  geom_point(data = zambia, aes(y = median(Diff_cpoint_hom_soc), x = median(Diff_dalys_hom_soc), color = "Zambia-HomeART"), size = 4, shape = zambia_shape) +

# SA: CAG, UAG, HomeART
geom_point(data = sa, aes(y = Diff_cpoint_cag_soc, x = Diff_dalys_cag_soc, color = "SouthAfrica-CAG"), alpha = ALPHA, size = 1) +
  geom_point(data = sa, aes(y = median(Diff_cpoint_cag_soc), x = median(Diff_dalys_cag_soc), color = "SouthAfrica-CAG"), size = 4, shape = sa_shape) +
  geom_point(data = sa, aes(y = Diff_cpoint_uag_soc, x = Diff_dalys_uag_soc, color = "SouthAfrica-UAG"), alpha = ALPHA, size = 1) +
  geom_point(data = sa, aes(y = median(Diff_cpoint_uag_soc), x = median(Diff_dalys_uag_soc), color = "SouthAfrica-UAG"), size = 4, shape = sa_shape) +
  geom_point(data = sa, aes(y = Diff_cpoint_hom_soc, x = Diff_dalys_hom_soc, color = "SouthAfrica-HomeART"), alpha = ALPHA, size = 1) +
  geom_point(data = sa, aes(y = median(Diff_cpoint_hom_soc), x = median(Diff_dalys_hom_soc), color = "SouthAfrica-HomeART"), size = 4, shape = sa_shape) +

# Synthesis: CAG, UAG, HomeART
geom_point(data = LMICs, aes(y = Diff_cpoint_cag_soc, x = Diff_dalys_cag_soc, color = "LMICs-CAG"), alpha = ALPHA, size = 1) + 
  geom_point(data = LMICs, aes(y = median(Diff_cpoint_cag_soc), x = median(Diff_dalys_cag_soc), color = "LMICs-CAG"), size = 4, shape = lmic_shape) +
  geom_point(data = LMICs, aes(y = Diff_cpoint_uag_soc, x = Diff_dalys_uag_soc, color = "LMICs-UAG"), alpha = ALPHA, size = 1) + 
  geom_point(data = LMICs, aes(y = median(Diff_cpoint_uag_soc), x = median(Diff_dalys_uag_soc), color = "LMICs-UAG"), size = 4, shape = lmic_shape) +
  geom_point(data = LMICs, aes(y = Diff_cpoint_hom_soc, x = Diff_dalys_hom_soc, color = "LMICs-HomeART"), alpha = ALPHA, size = 1) + 
  geom_point(data = LMICs, aes(y = median(Diff_cpoint_hom_soc), x = median(Diff_dalys_hom_soc), color = "LMICs-HomeART"), size = 4, shape = lmic_shape) 
  
# WPT
icer.plot <- icer.plot + 
  # WTP for SA
  geom_abline(slope = sa_WTP1, intercept = 0, color = "grey", linetype = "dashed", alpha = 0.7) + 
  geom_abline(slope = sa_WTP2, intercept = 0, color = "grey", linetype = "dashed", alpha = 0.7) +
  # WTP for other countries
  geom_abline(slope = WTP1, intercept = 0, color = "black", linetype = "dotted", alpha = 0.7) + 
  geom_abline(slope = WTP2, intercept = 0, color = "black", linetype = "dotted", alpha = 0.7) 
  
# color
icer.plot <- icer.plot + 
  scale_color_manual(values = c("Malawi-CAG" = "#b6d7a8", "Malawi-UAG" = "#6aa84f", "Malawi-HomeART" = "#8fce00",
                                "Zimbabwe-CAG" = "#9fc5e8", "Zimbabwe-UAG" = "#3d85c6", "Zimbabwe-HomeART" = "#349cfa",
                                "LMICs-CAG" = "#d9d2e9", "LMICs-UAG" = "#b8a1fb", "LMICs-HomeART" = "#9974f5",
                                "Zambia-CAG" = "#f9cb9c", "Zambia-UAG" = "#f6b26b", "Zambia-HomeART" = "#e69138",
                                "SouthAfrica-CAG" = "#ead1dc", "SouthAfrica-UAG" = "#faa2d0", "SouthAfrica-HomeART" = "#fa7ab9"),
                     guide = guide_legend(title = "Country-DSD"))

# format
icer.plot = icer.plot +
  theme(text = element_text(family = "Times New Roman")) +
  theme_minimal() + theme_bw() + 
  theme(panel.grid = element_blank()) # remove grid

ggsave(file=paste0("Figure2/", Sys.Date(), "-graph2-consolidated.png"), icer.plot, width = 7, height =5.25)
```

# Figure 3: ICER by time horizons
### v1: consolidated
```{r fig3-all-in-one}
rm(list=ls()) # clear the work space
library(ggplot2)
library(grid)
library(gridExtra)
library(cowplot)
```

##### Functions
```{r}
plot.fig3.allInOne = function(df, filename, 
                              WTP1 = 500, WTP2 = 750, WTP3 = 590, WTP4 = 3525, 
                              xlimits=c("5-year", "10-year", "20-year", "30-year", "40-year"), 
                              width=7, height=6, point_size=1, line_size=0.3) {
  # line and points
  fig3 = ggplot(df, aes(TimeHorizon, ICERs, col=Country.DSD, group=Country.DSD)) +
    geom_point(aes(shape = DSD), size=point_size) +
    geom_line(aes(linetype = DSD), linewidth=line_size)
  
  # WTP thresholds
  fig3 = fig3 +     
  geom_hline(yintercept = WTP1, linetype = "dotted", color = "black", linewidth=0.3) +
  geom_hline(yintercept = WTP2, linetype = "dotted", color = "black", linewidth=0.3) +
  geom_hline(yintercept = WTP3, linetype = "dotted", color = "grey", linewidth=0.3) +
  geom_hline(yintercept = WTP4, linetype = "dotted", color = "grey", linewidth=0.3)
  
  # format
  fig3 = fig3 +
    scale_x_discrete(limits = xlimits) +
    scale_color_manual(values = c("Malawi-CAG" = "#b6d7a8", "Malawi-UAG" = "#6aa84f", "Malawi-HomeART" = "#8fce00",
                                  "LMICs-CAG" = "#d9d2e9", "LMICs-UAG" = "#b8a1fb", "LMICs-HomeART" = "#9974f5",
                                  "Zambia-CAG" = "#f9cb9c", "Zambia-UAG" = "#f6b26b", "Zambia-HomeART" = "#e69138",
                                  "SouthAfrica-CAG" = "#ead1dc", "SouthAfrica-UAG" = "#faa2d0", "SouthAfrica-HomeART" = "#fa7ab9")) +
  labs(y = "ICERs", x = "Simulation time horizons", title = "ICERs of DSD compared to SoC by simulation horizons") + 
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank()) # remove grid
  
  # save file 
  ggsave(file=paste0("Figure3/", Sys.Date(), "-", filename), fig3, width = width, height = height)
}
```

##### Plot
```{r}
path = getwd()
df = read.csv(paste0(path, "/Figure3/long_df.csv"))
plot.fig3.allInOne(df=df, WTP1=0, WTP2=0, WTP3=0, WTP4=0, filename = "graph3-consolidated.png")
```

### v2: by country
```{r set-up}
rm(list=ls()) # clear the work space
library(ggplot2)
library(grid)
library(gridExtra)
library(cowplot)
```

##### Functions
```{r fig3-by_country-func}
plot.fig3.byCountry = function(df, countryname, WTP1=590, WTP2=3525, width=4, height=5, point_size=1, line_size=0.3, ylim=13000, legend_position="none") {
  # line and points
  fig3 = ggplot(df, aes(TimeHorizon, ICERs, color=DSD, group=Country.DSD)) +
    geom_point(aes(shape = DSD), size=point_size) +
    geom_line(aes(linetype = DSD), size=line_size)
  
  # WTP thresholds
  # WTP1 = 500, WTP2 = 750, WTP3 = 590, WTP4 = 3525
  fig3 = fig3 +     
  geom_hline(yintercept = WTP1, linetype = "dotted", color = "grey", linewidth=0.3) +
  geom_hline(yintercept = WTP2, linetype = "dotted", color = "grey", linewidth=0.3)
  
  # format
  fig3 = fig3 +
    scale_x_discrete(limits = c("5-year", "10-year", "20-year", "30-year", "40-year")) +
    labs(y = "ICERs", x = "Simulation time horizons", title = countryname) + 
    theme_minimal() +
    theme_bw() +
    coord_cartesian(ylim = c(0, ylim)) + 
    theme(legend.position = legend_position) + 
    theme(panel.grid = element_blank()) # remove grid
  
  # change font size
  fig3 = fig3 +
    theme(
  axis.title = element_text(size = 8),    # Change axis title font size
  plot.title = element_text(size = 10)     # Change plot title font size
)
}
```

##### Plot
```{r fig3-by_country-plot}
# Read in files
path = getwd()
zambia = read.csv(paste0(path, "/Figure3/long_df-Zambia.csv"))
sa = read.csv(paste0(path, "/Figure3/long_df-SA.csv"))
ssa = read.csv(paste0(path, "/Figure3/long_df-SSA.csv"))
malawi = read.csv(paste0(path, "/Figure3/long_df-Malawi.csv"))

# plots
pzambia = plot.fig3.byCountry(df=zambia, countryname = "Zambia", WTP1=500, WTP2=750) 
pmalawi = plot.fig3.byCountry(df=malawi, countryname = "Malawi", WTP1=500, WTP2=750) 
pssa = plot.fig3.byCountry(df=ssa, countryname = "LMICs", WTP1=500, WTP2=750) 
psa = plot.fig3.byCountry(df=sa, countryname = "SouthAfrica", WTP1=590, WTP2=3525) 

# save
legend <- get_legend(plot.fig3.byCountry(df=zambia, countryname = "Zambia", legend_position="right"))
grid.arrange(psa, pzambia ,pmalawi, pssa, legend, 
             layout_matrix=rbind(c(1,1,2,2,5), c(3,3,4,4,5)))
g <- arrangeGrob(psa, pzambia ,pmalawi, pssa, legend,
             layout_matrix=rbind(c(1,1,2,2,5), c(3,3,4,4,5)),
             top = textGrob("ICERs by time horizons", gp=gpar(fontsize=16,font=2)))
ggsave(file=paste0("Figure3/", Sys.Date(), "-graph3-byCountry.png"), g, width = 8, height =6) #saves g
```

# Figure 4: One way SA
```{r setwd_library}
rm(list=ls()) # clear the work space
library(ggplot2)
library(dplyr)
library(tidyverse)
library(gridExtra)
library(grid)
library(patchwork)
```
### Functions
```{r func_oneway_SA}
plot_sa = function(data, dsd_name, WTP1, WTP2, WTP_color, WTP_alpha, bar_width){
  ggplot(data) +
  geom_rect(aes(xmin = OutcomeRangeMin, xmax = PointEstimate,
                ymin = as.numeric(factor(Scenario)) - bar_width, ymax = as.numeric(factor(Scenario)) + bar_width), fill="#00468B") +
  geom_rect(aes(xmin = PointEstimate, xmax = OutcomeRangeMax,
                ymin = as.numeric(factor(Scenario)) - bar_width, ymax = as.numeric(factor(Scenario)) + bar_width), fill="#ED2200") +
  labs(title = dsd_name, x = "ICERs", y = "Scenarios") +
  geom_vline(xintercept = data$PointEstimate, linetype = "dashed", color = "black") +
  geom_vline(xintercept = WTP1, linetype = "solid", color = WTP_color, alpha=WTP_alpha) +
  geom_vline(xintercept = WTP2, linetype = "solid", color = WTP_color, alpha=WTP_alpha) +
  theme(legend.position = "right", legend.title = element_blank()) +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(), # change x or y grid, use panel.grid.major.x / panel.grid.minor.x
        axis.title.y = element_blank(), axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        axis.line = element_line(color="black", size=0.4))
}

plot_one_way_sa = function(data, country_name, WTP1=500, WTP2=750, WTP_color="#cca259", WTP_alpha=0.7, bar_width=0.2){
  cag = data %>% filter(DSD == "CAG") %>% mutate(Diff = abs(OutcomeRangeMax - OutcomeRangeMin))
  cag$Scenario <- factor(cag$Scenario, levels = cag$Scenario[order(cag$Diff, decreasing = TRUE)]) # reorder
  uag = data %>% filter(DSD == "UAG") %>% mutate(Diff = abs(OutcomeRangeMax - OutcomeRangeMin))
  uag$Scenario <- factor(uag$Scenario, levels = uag$Scenario[order(uag$Diff, decreasing = TRUE)]) # reorder
  home = data %>% filter(DSD == "HomeART") %>% mutate(Diff = abs(OutcomeRangeMax - OutcomeRangeMin))
  home$Scenario <- factor(home$Scenario, levels = home$Scenario[order(home$Diff, decreasing = TRUE)]) # reorder

  # plots
  plot1 = ggplot(cag) +
    geom_rect(aes(xmin = OutcomeRangeMin, xmax = PointEstimate,
                  ymin = as.numeric(factor(Scenario)) - bar_width, ymax = as.numeric(factor(Scenario)) + bar_width), fill="#00468B") +
    geom_rect(aes(xmin = PointEstimate, xmax = OutcomeRangeMax,
                  ymin = as.numeric(factor(Scenario)) - bar_width, ymax = as.numeric(factor(Scenario)) + bar_width), fill="#ED2200") +
    labs(title = paste0(country_name, ": CAG"), x = "ICERs", y = "Scenarios") +
    geom_vline(xintercept = cag$PointEstimate, linetype = "dashed", color = "black") +
    geom_vline(xintercept = WTP1, linetype = "solid", color = WTP_color, alpha=WTP_alpha) +
    geom_vline(xintercept = WTP2, linetype = "solid", color = WTP_color, alpha=WTP_alpha) +
    scale_y_continuous(breaks = as.numeric(factor(cag$Scenario)), labels = cag$Scenario) +
    # scale_color_manual(values = c("#00468B","#ED2200"),labels = c("Low value","High value"))+
    theme(legend.position = "right", legend.title = element_blank()) +
    theme_minimal() + theme_bw() +
    theme(panel.grid = element_blank(), # change x or y grid, use panel.grid.major.x / panel.grid.minor.x
          axis.line = element_line(color="black", size=0.4))

  plot2 = plot_sa(data=uag, dsd_name="UAG", WTP1=WTP1, WTP2=WTP2, WTP_color=WTP_color, WTP_alpha=WTP_alpha, bar_width=bar_width)
  plot3 = plot_sa(data=home, dsd_name="HomeART", WTP1=WTP1, WTP2=WTP2, WTP_color=WTP_color, WTP_alpha=WTP_alpha, bar_width=bar_width)

  combined_plots <- plot1 | plot2 | plot3 
  g = combined_plots
  return(g)
  # ggsave(file=paste0(path, "/Figure4/", country_name, "OneWaySA", ".png"), g, width = 12, height = 3)
}
```

### Plot
```{r}
path = getwd()

malawi = read.csv(paste0(path, "/Figure4/SA_Malawi.csv"))
pmalawi=plot_one_way_sa(data = malawi, country_name="Malawi",)
zambia = read.csv(paste0(path, "/Figure4/SA_Zambia.csv"))
pzambia=plot_one_way_sa(data = zambia, country_name="Zambia")
sa = read.csv(paste0(path, "/Figure4/SA_SouthAfrica.csv"))
psa=plot_one_way_sa(data = sa, country_name="SouthAfrica", WTP1 = 590, WTP2 = 3525)
synthesis = read.csv(paste0(path, "/Figure4/SA_Synthesis.csv"))
pssa=plot_one_way_sa(data = synthesis, country_name="LMICs")

combined_fig = psa / pzambia / pmalawi /pssa
ggsave(file=paste0("Figure4/", Sys.Date(), "-graph4-OneWaySA.png"), combined_fig, width=10, height=10) 
```
